The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-06 writing/draft3/draft8.tex
writing
and mainly moving more literature

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature including indicators of floods. Only some of them were found significant in our models. The significant measures include: Total seasonal precipitation and its squared values, average seasonal temperature, coefficient of variation of seasonal precipitation, standard deviation of average seasonal temperature \footnote{In case of temperature, we used standard deviation rather than coefficient of variation because temperature is measured on an interval scale and the coefficient of variation does not have any meaning for this type of data. },  maximum length of dry spell in number of days and the number of dry spell lasting for four days or more (a dry day is defined as day with precipitation less than $1$mm). We did not include squared values of the average seasonal temperature as it was not significant.
\subsection{Statistical approach}

@@

>>>>

Following the procedure described above, we calculated a number of previously used characteristics of precipitation and temperature including indicators of floods. Only some of them were found significant in our models. The significant measures include: Total seasonal precipitation and its squared values, average seasonal temperature, coefficient of variation of seasonal precipitation, standard deviation of average seasonal temperature \footnote{In case of temperature, we used standard deviation rather than coefficient of variation because temperature is measured on an interval scale and the coefficient of variation does not have any meaning for this type of data. },  maximum length of dry spell in number of days and the number of dry spell lasting for four days or more (a dry day has been defined as a day when precipitation didn't exceed $1$mm). We did not include squared values of the average seasonal temperature as it was not significant.
\subsection{Statistical approach}

@@

To find the most suitable set of predictors, we adopted a step-down model building approach using the Satterthwaite's method to determine the p-values of the individual t-test \cite{lmerTest}. That is, we started by including of all possible weather measures in both fixed effects and random effects and we consequently removed the insignificant ones until we got model with only significant fixed and random effects. For both fixed and random effects we considered the level of significance $\alpha=0.05$.
